---
title: "p8105_nr2774"
output: github_document
---

### Problem 1

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(rvest)
library(purrr)
library(ggplot2)
library(patchwork)
library(broom.mixed)
library(dplyr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```



### Problem 2 

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. For this problem, limit your analysis those for whom victim_race is white or black. Be sure that victim_age is numeric.

For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; 

# and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

# Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims.

# Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

# Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.


```{r}
# why do we have to apply group by?
# tidying dataset 
df = read_csv(file = "data/homicide-data.csv") |> 
    janitor::clean_names() |>
    mutate(city_state = str_c(city, state, sep = ","),
           homicide_binary = ifelse(disposition == "Closed by arrest",1,0),
           victim_age = as.numeric(victim_age),
           victim_race =as.factor(victim_race)) |> 
    group_by(city_state) |> 
    filter(city_state != "Dallas,TX" & city_state != "Tulsa,AL" & city_state != "Phoenix,AZ" & city_state != "Kansas City,MO") |>
    filter(victim_race == "White" | victim_race == "Black") |> 
    filter(!is.na(victim_age))
    
```

```{r}
baltimore_df = df |> 
    filter(city_state == "Baltimore,MD") 

baltimore_glm = 
    glm(data = baltimore_df, homicide_binary ~ victim_age + victim_sex + victim_race, family = binomial()) |> broom::tidy() |> 
    mutate(
    OR = exp(estimate),
    lower_ci = exp(estimate - 1.96 * std.error),
    upper_ci = exp(estimate + 1.96 * std.error)
  ) |> 
  select(term, estimate, OR, lower_ci,upper_ci ) |>
    filter(term == "victim_sexMale") |> 
    knitr::kable(digits = 3)
baltimore_glm

```

```{r}
all_state_function = function(df) {
    glm(data = df, homicide_binary ~ victim_age + victim_sex + victim_race, family = binomial()) |> broom::tidy() |> 
    mutate(
    OR = exp(estimate),
    lower_ci = exp(estimate - 1.96 * std.error),
    upper_ci = exp(estimate + 1.96 * std.error)
  ) |> 
  select(term, estimate, OR, lower_ci,upper_ci ) |>
    filter(term == "victim_sexMale") 
}
    

all_state_glm = df |>
    nest(mini_data = c(-13)) |> 
    mutate(
    state_glm = map(.x = mini_data, all_state_function)) %>%
    select(-mini_data) |> 
    unnest(state_glm)

```

```{r}
all_state_glm %>% 
  ggplot(aes(x = fct_reorder(city_state, OR), y = OR)) +
  geom_point() + 
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))+
  labs(
    x = "City and State Names",
    y = "Adjusted Odd Ratio",
    title = "Estimated ORs and CIs for all cities"
  )
```

### Problem 3

In this problem, you will analyze data gathered to understand the effects of several variables on a child’s birthweight. This dataset, available here, consists of roughly 4000 children and includes the following variables:

Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

Note that although we expect your model to be reasonable, model building itself is not a main idea of the course and we don’t necessarily expect your model to be “optimal”.

```{r}
birthweight_df = 
  read_csv("data/birthweight.csv") |> 
    janitor::clean_names() %>%
  mutate(
    babysex = case_when(
      babysex == 1 ~ "Male",
      babysex == 2 ~ "Female"
    )) %>% mutate(
          menarche = as.factor(menarche),
parity = as.factor(parity),
frace = as.factor(frace),
mrace = as.factor(mrace),
malform = as.factor(malform),
babysex = as.factor(babysex))

sapply(birthweight_df, function(x) sum(is.na(x)))         

```
There are no missing values found in the output. For the better understanding and readability babies sex are modified as Male and Female. There are `r nrow(birthweight_df)` of rows and `r ncol(birthweight_df)`  of colums in the birthweight data frame. Variables were chosen based on the 10 factors that affect a baby's birth weight articles on the internet. 

```{r}
model_birthweight_1 = 
    lm(data = birthweight_df , bwt ~ parity + frace + malform + malform + babysex + gaweeks)

model_birthweight_1|> broom::tidy()

```

```{r}
library(modelr)
birthweight_df %>% 
  add_residuals(model_birthweight_1)|> 
  add_predictions(model_birthweight_1) |>  
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.3) +
  labs(
    title = "",
    x = "Predicted",
    y = "Residuals"
    ) +
  theme(plot.title = element_text(hjust = 0.5))+
  geom_line(aes(y = 0), color = "blue")

```

The residuals "bounce randomly" around the 0 line. This suggests that the assumption that the relationship is linear is reasonable.
The residuals roughly form a "horizontal band" around the 0 line. This suggests that the variances of the error terms are equal.
No one residual "stands out" from the basic random pattern of residuals. This suggests that there are no outliers.

```{r}



```

