---
title: "p8105_nr2774"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(rvest)
library(purrr)
library(ggplot2)
library(patchwork)
library(broom.mixed)
library(dplyr)
library(modelr)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

### Problem 1

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 

### Problem 2 

```{r}
# tidying dataset 
df = read_csv(file = "data/homicide-data.csv") |> 
    janitor::clean_names() |>
    mutate(city_state = str_c(city, state, sep = ","),
           homicide_binary = ifelse(disposition == "Closed by arrest",1,0),
           victim_age = as.numeric(victim_age),
           victim_race =as.factor(victim_race)) |> 
    group_by(city_state) |> 
    filter(city_state != "Dallas,TX" & city_state != "Tulsa,AL" & city_state != "Phoenix,AZ" & city_state != "Kansas City,MO") |>
    filter(victim_race == "White" | victim_race == "Black") |> 
    filter(!is.na(victim_age))
    
```

```{r}
baltimore_df = df |> 
    filter(city_state == "Baltimore,MD") 

baltimore_glm = 
    glm(data = baltimore_df, homicide_binary ~ victim_age + victim_sex + victim_race, family = binomial()) |> broom::tidy() |> 
    mutate(
    OR = exp(estimate),
    lower_ci = exp(estimate - 1.96 * std.error),
    upper_ci = exp(estimate + 1.96 * std.error)
  ) |> 
  select(term, estimate, OR, lower_ci,upper_ci ) |>
    filter(term == "victim_sexMale") |> 
    knitr::kable(digits = 3)
baltimore_glm

```

```{r}
all_state_function = function(df) {
    glm(data = df, homicide_binary ~ victim_age + victim_sex + victim_race, family = binomial()) |> broom::tidy() |> 
    mutate(
    OR = exp(estimate),
    lower_ci = exp(estimate - 1.96 * std.error),
    upper_ci = exp(estimate + 1.96 * std.error)
  ) |> 
  select(term, estimate, OR, lower_ci,upper_ci ) |>
    filter(term == "victim_sexMale") 
}
    

all_state_glm = df |>
    nest(mini_data = c(-13)) |> 
    mutate(
    state_glm = map(.x = mini_data, all_state_function)) %>%
    select(-mini_data) |> 
    unnest(state_glm)

```

```{r}
all_state_glm %>% 
  ggplot(aes(x = fct_reorder(city_state, OR), y = OR)) +
  geom_point() + 
  geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))+
  labs(
    x = "City and State Names",
    y = "Adjusted Odd Ratio",
    title = "Estimated ORs and CIs for all cities"
  )
```

### Problem 3

```{r}
birthweight_df = 
  read_csv("data/birthweight.csv") |> 
    janitor::clean_names() %>%
  mutate(
    babysex = case_when(
      babysex == 1 ~ "Male",
      babysex == 2 ~ "Female"
    )) %>% mutate(
          menarche = as.factor(menarche),
parity = as.factor(parity),
frace = as.factor(frace),
mrace = as.factor(mrace),
malform = as.factor(malform),
babysex = as.factor(babysex))

sapply(birthweight_df, function(x) sum(is.na(x)))         

```
There are no missing values found in the output. For the better understanding and readability babies sex are modified as Male and Female. There are `r nrow(birthweight_df)` of rows and `r ncol(birthweight_df)`  of colums in the birthweight data frame. Variables were chosen based on the 10 factors that affect a baby's birth weight articles on the internet. 

```{r}
model_proposed = 
    lm(data = birthweight_df , bwt ~ frace + malform + malform + babysex + gaweeks)

model_proposed |> broom::tidy()

```

```{r}

birthweight_df %>% 
  add_residuals(model_proposed) |> 
  add_predictions(model_proposed) |>  
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.3) +
  labs(
    title = "",
    x = "Predicted",
    y = "Residuals"
    ) +
  theme(plot.title = element_text(hjust = 0.5))+
  geom_line(aes(y = 0), color = "blue")

```

* The residuals "bounce randomly" around the 0 line. This suggests that the assumption that the relationship is linear is reasonable.
* The residuals roughly form a "horizontal band" around the 0 line. This suggests that the * variances of the error terms are equal.
* Although there are some residual "stands out" from the basic random pattern of residuals. This suggests that there are some outliers.

* Constant variance assumption does not work here. It means that when I run hypothesis test, i should be aware of non-constant variance.  

```{r}

model_1 = 
    lm(data = birthweight_df , bwt ~ blength + gaweeks)

model_1|> broom::tidy()


# Interaction effect
model_2 =
    lm(data = birthweight_df, bwt ~ bhead + blength + 
           babysex + bhead*blength + blength*babysex + 
           bhead*babysex + bhead*blength*babysex)

model_2|> broom::tidy()
```

```{r}
cv_df =
  crossv_mc(birthweight_df, 100) %>% 
    mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) |> 
    mutate(
        model_10 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
        model_11 = map(train, ~lm(bwt ~ bhead + blength + 
           babysex + bhead*blength + blength*babysex + 
           bhead*babysex + bhead*blength*babysex, data = .x)),
    model_proposed = map(train, ~lm(bwt ~frace + malform + malform + babysex + gaweeks, data = .x))) %>% 
    mutate(
    rmse_model_10 = map2_dbl(.x = model_10, test, ~rmse(model = .x, data = .y)),
    rmse_model_11 = map2_dbl(.x = model_11, test, ~rmse(model = .x, data = .y)),
    rmse_model_proposed = map2_dbl(.x = model_proposed, test, ~rmse(model = .x, data = .y)))

```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse, color = model)) + geom_violin() + 
    geom_boxplot(alpha = 0.5, color = "blue")+
  labs(
    x = "Models",
    y = "RMSE",
    title = " RMSE distribution for 3 models "
  )+
  theme( plot.title = element_text(hjust = .5))

```

According to the RMSE plot, model 11 appears to be the best match compored to other two models with the lowest RSME value. Model_proposed performs the worst for this data ended up having the highest RMSE.